GNSS displacement detection based on Bayesian inference

### 2020-11-14 paper/manuscript.tex
add output code

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
In recent decades, GNSS has been widely used in navigation, surveying, and civil aviation as a positioning method. Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring, industrial measurement, and other fields. Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence.

>>>>

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
%GNSS在位移探测中扮演的角色，以及位移探测的要求
In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method. Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring, industrial measurement, and other fields. Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence. Displacement detection involves automatic identification of the time of displacement and determination of displacement. GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results.
